DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-06-29 ase2017/paper.tex
ase
Signed-off-by: aabate <aabate@cs.ox.ac.uk>

\title{DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox}

@@

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize stable and safe digital controllers 
for physical plants represented as linear time-invariant
systems with single-input and single-output. In particular, DSSynth synthesizes digital 
controllers w.r.t. the stability and safety specifications by taking into account finite word-length 
effects. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic and its rounding errors. 
Currently, there are two DSSynth toolbox versions: command-line and 
MATLAB application for synthesizing digital controllers for physical plants 
represented by transfer-function or state-space equations. The resulting toolbox 
enables application of program synthesis to real-world systems by control engineers.
\end{abstract}

@@

Control theory achieves the construction of reliable systems by 
offering mathematical guarantees about the stability and the desired 
performance of closed-loop dynamical systems, where states or outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a (designed) 
controller $C(z)$ should maintain a set of control objectives~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

There are various mathematical representations for digital control
systems,  e.g.,  difference  equations, transfer functions and state-space
equations. Here, linear time-invariant (LTI) systems 
with single-input and single-output (SISO) are considered and 
represented by transfer functions or state space equations. LTI systems 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded systems (e.g., robot manipulator, power plants 
and guidance system). The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials, respectively; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In state-space format, the digital control system represents the behavior 
of a system via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

 \end{tikzpicture}
}}
\caption{CEGIS with multi-staged verification}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

\tool can synthesize digital controllers for dynamic physical plants 
w.r.t. stability and safety, designed in MATLAB through transfer-function 
and state-space representations using the CEGIS approach.
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account implementation 
aspects (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate
 other controller properties (e.g., limit cycle).

>>>>

\title{DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants} 
% via MATLAB Toolbox}

@@

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer-function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

Control theory targets the construction of reliable systems by providing mathematical guarantees about the stability and the desired 
performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a (designed) 
controller $C(z)$ should steer~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

There are various mathematical representations for control 
systems,  e.g.,  transfer functions and state-space equations (difference or differential equations). 
Here, 
systems with a single input and a single output (SISO) are considered and 
represented by transfer functions or state-space LTI models. LTI models 
are used in several engineering applications to support non-trivial tasks when 
applied to embedded systems (e.g., robot manipulator, power plants 
and guidance system). The following expression presents the general form 
of a discrete plant or a digital controller based on the transfer function representation:
%
\begin{equation}
\small
\label{eq:transferfunction}
H(z)=\frac{B(z)}{A(z)}=\frac{b_{0}+b_{1}z^{-1}+...+b_{M}z^{-M}}{1+a_{1}z^{-1}+...+a_{N}z^{-N}},
\end{equation}
%
\noindent where $z^{-1}$ is called backward-shift operator; $A(z)$ and $B(z)$ are 
the denominator and numerator polynomials, respectively; and $N$ and $M$
represent the denominator and numerator polynomials order, respectively.
%
In state-space format, the digital control system represents the behavior 
of a system via a state evolution equation $x(n+1)$ and an instantaneous 
output equation $y(n)$, as follows:
%
\begin{equation}
\begin{split}
x(n+1) &= A x(n) + B u(n)
\\
y(n) &= C x(n) + D u(n), 
\end{split}\label{eq:ss-example}
\end{equation}

@@

 \end{tikzpicture}
}}
\caption{CEGIS with multi-staged verification \textcolor{red}{[make this fit the column]}}
\label{fig:CEGIS-precision-increment}
\end{figure}

@@

\tool can synthesize digital controllers for dynamic physical plants, 
represented in MATLAB through transfer-function and state-space,  
w.r.t. stability and safety, using the CEGIS approach. 
%
Given the current literature in controller synthesis, there is no other MATLAB toolbox 
for synthesizing stable digital controllers for physical plants, while taking into account all aspects of its digital implementation (fixed-point arithmetic). 
%
As future work, \tool will perform synthesis of other types of specifications (e.g., performance) 
and be combined with DSVerifier/DSValidator Toolboxes~\cite{issta2017,dsvalidator} to verify/validate 
other controller properties (e.g., presence of limit cycles).

\textcolor{red}{[Pls update CAV reference with details from proof of article just received from Springer. ]}
